A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-04-25 idetc2018_journal.tex
Merging into conference .tex

\begin{figure}
\begin{tabular}{cc}
  1)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol1.eps}}
    & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
  3)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol3.eps}}
    & 4)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol4.eps}}\\
  5)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol5.eps}}
    & 6)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol6.eps}} \\
  7)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol7.eps}}
    & 8)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol8.eps}}\\
\end{tabular}
\caption{First eight linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
\label{ex1_solns}
\end{figure}

@@

\bibliographystyle{purwar}
\bibliography{References}

>>>>

\begin{figure}
\begin{tabular}{cc}
  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
    & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
  3)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol3.eps}}
    & 4)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol4.eps}}\\
  5)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol5.eps}}
    & 6)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol6.eps}} \\
  7)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol7.eps}}
    & 8)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol8.eps}}\\
\end{tabular}
\caption{First eight linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
\label{ex1_solns}
\end{figure}

@@

\bibliographystyle{purwar}
\bibliography{References}
\newpage
\clearpage
\listoftables
\listoffigures
